Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-12-01 WSSSPE3/report/wg_appendix_training.tex
Update wg_appendix_training.tex
- resolved \katznote
- shifted timing to early 2016

While little training focuses specifically on this outcome \katznote{sustainable
software?}, a variety of training activities increase researcher awareness of
and engagement with software professionals and software engineering practices.
Research Software Engineers are being recognized as critical contributors to
high quality research; the pathway to acquire and master the relevant skills
is not yet clear; equally those skills required by researchers in general are
also not commonly understood nor routinely developed.

@@

\item During October, Nick Jones and Erin Robinson to draft WSSSPE3 report back.

\item Before December 2015, Nick Jones and Erin Robinson to call a meeting of
the broader group, to review key next steps.

\item First quarter 2016 -- if willing parties are identified, draft workshop proposal
and identify a relevant forum, including future WSSSPE events.

>>>>

While little training focuses specifically on sustainable
software, a variety of training activities increase researcher awareness of
and engagement with software professionals and software engineering practices.
Research Software Engineers are being recognized as critical contributors to
high quality research; the pathway to acquire and master the relevant skills
is not yet clear; equally those skills required by researchers in general are
also not commonly understood nor routinely developed.

@@

\item October through December, Nick Jones and Erin Robinson to draft WSSSPE3 report back.

\item Before February 2016, Nick Jones and Erin Robinson to call a meeting of
the broader group, to review key next steps.

\item Second quarter 2016 -- if willing parties are identified, draft workshop proposal
and identify a relevant forum, including future WSSSPE events.
